Reduced plasticity and relative variance in physiological rates of ectotherm populations under climate change

### 2024-05-19 ms.qmd
Editing some awkward sentences

Climate change is expected to result in warmer but also more variable thermal environments globally [@Suarez2023; @Easterling2000; @Ummenhofer2017]. Greater thermal variability in the past is predicted to result in strong selection pressures that lead to genetic adaptation and/or the evolution of adaptive phenotypic plasticity -- both of which are considered important for population resilience to contemporary human-induced climate change [@Seebacher2015-wi; @Merila2014; @Chevin2015; @Chevin2017; @Chevin2010; @Nunney2016; @seebacher2023can; @cooke2021one]. Without plasticity or adaptation, high extinction rates are expected unless organisms can migrate to track suitable habitats [@Cahill2012; @Nunney2016].

>>>>

Climate change is expected to result in warmer but also more variable thermal environments globally [@Suarez2023; @Easterling2000; @Ummenhofer2017]. Greater thermal variability is predicted to result in strong selection pressures that lead to genetic adaptation and/or the evolution of adaptive phenotypic plasticity -- both of which are considered important for population resilience to contemporary human-induced climate change [@Seebacher2015-wi; @Merila2014; @Chevin2015; @Chevin2017; @Chevin2010; @Nunney2016; @seebacher2023can; @cooke2021one]. Without plasticity or adaptation, high extinction rates are expected unless organisms can migrate to track suitable habitats [@Cahill2012; @Nunney2016].
